manuscript_outline

### 2025-07-18 docs/manuscript/paper.Rmd
rerender after fixing bib
rerender with copy edits

keywords: developmental phenology, hatchR, local adaptation, R, reaction norm, Shiny

@@

**hatchR** is an open-source software environment distributed via CRAN and additional details are hosted at software website (<https://bmait101.github.io/hatchR/>). Reproducible methods for this manuscript are available at the manuscript github (<https://github.com/morgan-sparks/hatchR_nonfish>) in the `paper.Rmd` file. The repository will become public and publicly archived with a DOI at acceptance of the manuscript.

@@

fmt <- "~R^2 ==  %.4f"
lab1 <- sprintf(fmt, ascaphus_mod$r_squared)
p1 <- ascaphus_mod$pred_plot +
  labs(x = "Incubation Temperature (°C)", y = "Days to Hatch") +
  lims(y = c(0, 50)) +
  annotate("text", x = 10, y = c(35), label = c(lab1),  hjust = 0, parse = TRUE)

@@

: Putative sources for effective value parameterization using `fit_model()` in **hatchR.** This compilation spans amphibians, reptiles, aquatic and terrestrial insects, crustaceans, copepods, squids and octopuses, and starfishes. @while2018 and @pritchard1987 are broader reviews with multiple species and are flagged as not yet vetted for full reciprocal model implementation. Users may need to extract or adapt published equations to align with the effective value framework.

>>>>

keywords: developmental phenology; hatchR; local adaptation,;R, reaction norm; Shiny

@@

**hatchR** is an open-source software environment distributed via CRAN and additional details are hosted at software website (<https://bmait101.github.io/hatchR/>). Reproducible methods for this manuscript are available at the manuscript github (<https://github.com/morgan-sparks/hatchR_nonfish>) in the `paper.Rmd` file. The repository will become publicly archived with a DOI at acceptance of the manuscript.

@@

fmt <- "~R^2 ==  %.4f"
lab1 <- sprintf(fmt, ascaphus_mod$r_squared)
p1 <- ascaphus_mod$pred_plot +
  labs(x = "Incubation Temperature (°C)", y = "Days to Hatch") +
  lims(y = c(0, 50)) +
  annotate("text", x = 10, y = c(35), label = c(lab1),  hjust = 0, parse = TRUE) +
  theme_classic(base_size = 16)

@@

: Putative sources for effective value parameterization using `fit_model()` in **hatchR** for a broad array of taxa**.** @while2018 and @pritchard1987 are broader reviews with multiple species and are flagged as not yet vetted for full reciprocal model implementation. Users may need to extract or adapt published equations to align with the effective value framework.
